### 2015-01-14 fundamentals/impl.tex
got rid of 'assistance' in the simulation assistance title

A modular, agent-based approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice to 
build \Cyclus on open source libraries in modern programming languages enables 
both remote and multiprocess execution on a number of platforms. This section begins by 
describing the general design features that make \Cyclus both flexible and powerful:
cluster-ready software and dynamic libraries.  Next, the framework using an
\gls{ABM} paradigm, which provides an expansion in performance beyond typical systems dynamics
capabilities, is described, focusing on agent interchangeability and the 
implementation of the region-institution-facility hierarchy. 
Next, the discrete treatment of objects is discussed in terms of both
resources and materials and time via the \gls{DRE}.
Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.
Lastly, the methods for quality assurance are outlined.
These features provide a solid foundation on which to build an interconnected community 
of archetype developers with diverse backgrounds and simulation goals.

@@

\subsection{Simulation Assistance}
So that users and developers can build working simulations
in the shortest time possible, the \Cyclus ecosystem provides the fundamental 
building blocks: basic archetypes and a toolkit of commonly needed functions.
The \Cycamore library provides a suite of fundamental Region, Institution, and 
Facility archetypes, while the \Cyclus toolkit provides assistance to 
developers.

>>>>

A modular, agent-based approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice to 
build \Cyclus on open source libraries in modern programming languages enables 
both remote and multiprocess execution on a number of platforms. This section begins by 
describing the general design features that make \Cyclus both flexible and powerful:
cluster-ready software and dynamic libraries.  Next, the framework using an
\gls{ABM} paradigm, which provides an expansion in performance beyond typical systems dynamics
capabilities, is described, focusing on agent interchangeability and the 
implementation of the region-institution-facility hierarchy. 
Next, the discrete treatment of objects is discussed in terms of both
resources and materials and time via the \gls{DRE}.
Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.
Lastly, the methods for quality assurance are outlined.

@@

\subsection{Simulation Support}
So that users and developers can build working simulations
in the shortest time possible, the \Cyclus ecosystem provides the fundamental 
building blocks: basic archetypes and a toolkit of commonly needed functions.
The \Cycamore library provides a suite of fundamental Region, Institution, and 
Facility archetypes, while the \Cyclus toolkit provides assistance to 
developers.
